Changes in trip-making frequency by mode during the COVID-19 emergency in Bangladesh

### 2020-10-23 Frequency-of-Travel-by-Mode-COVID-19-Bangladesh/Frequency-of-Travel-by-Mode-COVID-19-Bangladesh.tex
v2 Started working on revisions after reviews

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={An exploratory analysis of changes in trip-making frequency by mode during the COVID-19 emergency in Bangladesh},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

% Pandoc header
\usepackage{float} \floatplacement{figure}{H}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

@@

  \title{An exploratory analysis of changes in trip-making frequency by mode
during the COVID-19 emergency in Bangladesh}
    \author[McMaster University]{Shaila Jamal}
   \ead{jamals16@mcmaster.ca} 
    \author[McMaster University]{Antonio Paez\corref{1}}
   \ead{paezha@mcmaster.ca} 
      \address[McMaster University]{School of Earth, Environment and Society, McMaster University, Hamilton,
ON, L8S 4K1, Canada}
      \cortext[1]{Corresponding Author}

  \begin{abstract}
  The COVID-19 pandemic has had a profound impact on mobility in every
  country and region around the world. Recent helps to illuminate some of
  the dimensions of change - however, the evidence is still scant in
  developing countries. The objective of this paper is to present an
  exploratory analysis of the changes in the frequency of trip-making by
  mode during the COVID-19 emergency in Bangladesh. The results confirm an
  overall loss of mobility in the form of reduced trip-making frequency by
  all modes, but the changes are not uniform across modes. In particular,
  there was a greater loss of mobility for bus, rickshaw, and CNG
  auto-rickshaw.
  \end{abstract}

@@

For the purpose of this paper, we use two questions that provide
information about trip-making frequency by eight modes of
transportation. The modes are \textbf{car}, \textbf{ridesharing} (e.g.,
Uber, Pathao), \textbf{rickshaw}, \textbf{CNG auto-rickshaw} (a
rickshaw-like vehicle powered by compressed natural gas), \textbf{bus},
motorcycle/scooter (hereafter just \textbf{motorcycle}),
\textbf{walking}, and \textbf{bicycle} (there was an additional
catch-all category \textbf{other} which we ignore here). Participants in
the survey used the following levels to report their frequency of
traveling by each mode both before and during COVID-19: \emph{Never},
\emph{Rarely}, \emph{Once a week}, \emph{2-3 trips per week}, \emph{4-5
trips per week}, \emph{Almost daily}. There are \(n=800\) responses in
the data set.

@@

Figure \ref{fig:column-plot-cases} shows the number of responses (out of
800) in each trip-making frequency class by mode of transportation. The
white bars and gray bars are for travel before and during the pandemic,
respectively. Considering travel before the pandemic, travel by
rickshaw, and bus were relatively common for many respondents (few
respondents reported \emph{never} using these modes). The mode most
commonly used on a quotidian basis was walk. In contrast, respondents
reported less frequent travel by car, ridesharing services, CNG
auto-rickshaw, motorcycle, and bicycle. During the pandemic, we see that
while there were reductions in mobility by car, motorcycle, and bicycle
(with more respondents reporting never traveling by these modes), the
changes were relatively minor.

@@

\caption{\label{tab:table-transitions}\label{tab:cross-tabulation} Cross-tabulation of counts of travel frequency by mode, before and during COVID-19}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrr}
\toprule
  & Never & Rarely & Once a week & 2-3 per week & 4-5 per week & Almost daily\\
\midrule
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{car}}\\
\hspace{1em}Never & 267 & 20 & 5 & 1 & 1 & 2\\
\hspace{1em}Rarely & 142 & 99 & 21 & 12 & 9 & 3\\
\hspace{1em}Once a week & 11 & 23 & 19 & 7 & 2 & 3\\
\hspace{1em}2-3 per week & 10 & 23 & 7 & 6 & 8 & 2\\
\hspace{1em}4-5 per week & 4 & 9 & 5 & 6 & 12 & 4\\
\hspace{1em}Almost daily & 6 & 15 & 6 & 10 & 0 & 20\\
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{rideshare}}\\
\hspace{1em}Never & 254 & 13 & 6 & 4 & 0 & 0\\
\hspace{1em}Rarely & 192 & 44 & 12 & 1 & 1 & 1\\
\hspace{1em}Once a week & 60 & 20 & 31 & 3 & 1 & 0\\
\hspace{1em}2-3 per week & 49 & 12 & 9 & 7 & 2 & 0\\
\hspace{1em}4-5 per week & 28 & 10 & 3 & 5 & 6 & 2\\
\hspace{1em}Almost daily & 14 & 3 & 4 & 1 & 0 & 2\\
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{rickshaw}}\\
\hspace{1em}Never & 51 & 9 & 6 & 0 & 1 & 0\\
\hspace{1em}Rarely & 64 & 70 & 18 & 4 & 3 & 1\\
\hspace{1em}Once a week & 36 & 38 & 45 & 9 & 3 & 3\\
\hspace{1em}2-3 per week & 34 & 36 & 18 & 29 & 6 & 4\\
\hspace{1em}4-5 per week & 21 & 30 & 7 & 16 & 15 & 8\\
\hspace{1em}Almost daily & 45 & 65 & 30 & 18 & 16 & 41\\
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{CNG auto-rickshaw}}\\
\hspace{1em}Never & 176 & 14 & 3 & 1 & 0 & 0\\
\hspace{1em}Rarely & 213 & 95 & 14 & 4 & 1 & 3\\
\hspace{1em}Once a week & 36 & 31 & 38 & 9 & 2 & 3\\
\hspace{1em}2-3 per week & 29 & 18 & 16 & 14 & 8 & 3\\
\hspace{1em}4-5 per week & 13 & 6 & 5 & 9 & 14 & 1\\
\hspace{1em}Almost daily & 8 & 7 & 2 & 0 & 0 & 4\\
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{bus}}\\
\hspace{1em}Never & 116 & 9 & 3 & 0 & 0 & 0\\
\hspace{1em}Rarely & 155 & 46 & 9 & 0 & 0 & 1\\
\hspace{1em}Once a week & 73 & 32 & 22 & 4 & 0 & 0\\
\hspace{1em}2-3 per week & 43 & 19 & 11 & 7 & 5 & 0\\
\hspace{1em}4-5 per week & 60 & 6 & 5 & 4 & 12 & 1\\
\hspace{1em}Almost daily & 103 & 21 & 10 & 11 & 2 & 10\\
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{motorcycle}}\\
\hspace{1em}Never & 467 & 22 & 12 & 3 & 1 & 8\\
\hspace{1em}Rarely & 44 & 38 & 13 & 10 & 0 & 4\\
\hspace{1em}Once a week & 11 & 11 & 34 & 3 & 3 & 3\\
\hspace{1em}2-3 per week & 13 & 6 & 6 & 15 & 4 & 2\\
\hspace{1em}4-5 per week & 6 & 4 & 0 & 4 & 14 & 3\\
\hspace{1em}Almost daily & 1 & 3 & 2 & 4 & 3 & 23\\
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{walk}}\\
\hspace{1em}Never & 17 & 7 & 3 & 4 & 0 & 2\\
\hspace{1em}Rarely & 26 & 53 & 13 & 6 & 2 & 4\\
\hspace{1em}Once a week & 12 & 19 & 54 & 9 & 4 & 2\\
\hspace{1em}2-3 per week & 10 & 14 & 12 & 26 & 13 & 4\\
\hspace{1em}4-5 per week & 7 & 3 & 7 & 11 & 16 & 8\\
\hspace{1em}Almost daily & 46 & 73 & 40 & 49 & 27 & 197\\
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{bicycle}}\\
\hspace{1em}Never & 504 & 22 & 7 & 4 & 2 & 4\\
\hspace{1em}Rarely & 59 & 43 & 20 & 4 & 2 & 4\\
\hspace{1em}Once a week & 14 & 13 & 21 & 3 & 2 & 1\\
\hspace{1em}2-3 per week & 3 & 4 & 5 & 7 & 2 & 0\\
\hspace{1em}4-5 per week & 2 & 2 & 4 & 1 & 9 & 3\\
\hspace{1em}Almost daily & 7 & 1 & 1 & 1 & 3 & 16\\
\bottomrule
\end{tabular}}
\end{table}

The frequency of trip-making by other modes changed more noticeably: the
frequency of travel by ridesharing services, rickshaw, CNG
auto-rickshaw, and bus collapsed, with vastly more respondents reporting
never using these modes during the pandemic than before. The frequency
of walking trips also decreased (fewer respondents report walking almost
daily), but the reductions in mobility were not so heavily concentrated
at the bottom of the scale.

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Changes in trip-making frequency by mode during the COVID-19 emergency in Bangladesh},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

% Pandoc header
\usepackage{float} \usepackage{xcolor} \floatplacement{figure}{H}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

@@

  \title{Changes in trip-making frequency by mode during the COVID-19 emergency
in Bangladesh}
    \author[McMaster University]{Shaila Jamal}
   \ead{jamals16@mcmaster.ca} 
    \author[McMaster University]{Antonio Paez\corref{1}}
   \ead{paezha@mcmaster.ca} 
      \address[McMaster University]{School of Earth, Environment and Society, McMaster University, Hamilton,
ON, L8S 4K1, Canada}
      \cortext[1]{Corresponding Author}

  \begin{abstract}
  The COVID-19 pandemic has had a profound impact on mobility in every
  country and region around the world. Recent helps to illuminate some of
  the dimensions of change - however, the evidence is still scant in
  developing countries. The objective of this paper is to present an
  exploratory analysis of the changes in the frequency of trip-making by
  mode during the COVID-19 emergency in Bangladesh. The results confirm an
  overall loss of mobility in the form of reduced trip-making frequency by
  all modes, but the changes are not uniform across modes. In particular,
  there was a greater loss of mobility for bus, rickshaw, and CNG
  auto-rickshaw, and some adoption of walking during the pandemic.
  \end{abstract}

@@

For the purpose of this paper, we use two questions that provide
information about trip-making frequency by eight modes of
transportation. The modes are \textbf{car}, \textbf{ride-hailing} (e.g.,
Uber, Pathao), \textbf{rickshaw}, \textbf{CNG auto-rickshaw} (a
rickshaw-like vehicle powered by compressed natural gas), \textbf{bus},
motorcycle/scooter (hereafter just \textbf{motorcycle}),
\textbf{walking}, and \textbf{bicycle} (there was an additional
catch-all category \textbf{other} which we ignore here). Participants in
the survey used the following levels to report their frequency of
traveling by each mode both before and during COVID-19: \emph{Never},
\emph{Rarely}, \emph{Once a week}, \emph{2-3 trips per week}, \emph{4-5
trips per week}, \emph{Almost daily}. There are \(n=800\) responses in
the data set.

@@

Figure \ref{fig:column-plot-cases} shows the number of responses (out of
800) in each trip-making frequency class by mode of transportation. The
white bars and gray bars are for travel before and during the pandemic,
respectively. Considering travel before the pandemic, travel by
rickshaw, and bus were relatively common for many respondents (few
respondents reported \emph{never} using these modes). The mode most
commonly used on a quotidian basis was walk. In contrast, respondents
reported less frequent travel by car, ride-hailing services, CNG
auto-rickshaw, motorcycle, and bicycle. During the pandemic, we see that
while there were reductions in mobility by car, motorcycle, and bicycle
(with more respondents reporting never traveling by these modes), the
changes were relatively minor.

@@

\caption{\label{tab:table-transitions}\label{tab:cross-tabulation} Cross-tabulation of counts of travel frequency by mode, before and during COVID-19}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{6}{c}{During} \\
\cmidrule(l{3pt}r{3pt}){2-7}
Before & Never & Rarely & Once a week & 2-3 times per week & 4-5 times per week & Almost daily\\
\midrule
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{car}}\\
\hspace{1em}Never & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{267}}} & \cellcolor[HTML]{F79242}{\textcolor{white}{\textbf{20}}} & \cellcolor[HTML]{FBA238}{\textcolor{white}{\textbf{5}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{1}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{1}}} & \cellcolor[HTML]{FCA537}{\textcolor{white}{\textbf{2}}}\\
\hspace{1em}Rarely & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{142}}} & \cellcolor[HTML]{7D03A8}{\textcolor{white}{\textbf{99}}} & \cellcolor[HTML]{F1824C}{\textcolor{white}{\textbf{21}}} & \cellcolor[HTML]{F79442}{\textcolor{white}{\textbf{12}}} & \cellcolor[HTML]{F99A3E}{\textcolor{white}{\textbf{9}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{3}}}\\
\hspace{1em}Once a week & \cellcolor[HTML]{C13B82}{\textcolor{white}{\textbf{11}}} & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{23}}} & \cellcolor[HTML]{5801A4}{\textcolor{white}{\textbf{19}}} & \cellcolor[HTML]{E26660}{\textcolor{white}{\textbf{7}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{2}}} & \cellcolor[HTML]{F9993E}{\textcolor{white}{\textbf{3}}}\\
\hspace{1em}2-3 times per week & \cellcolor[HTML]{CA457A}{\textcolor{white}{\textbf{10}}} & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{23}}} & \cellcolor[HTML]{E26660}{\textcolor{white}{\textbf{7}}} & \cellcolor[HTML]{E97257}{\textcolor{white}{\textbf{6}}} & \cellcolor[HTML]{DB5C68}{\textcolor{white}{\textbf{8}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{2}}}\\
\hspace{1em}4-5 times per week & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{4}}} & \cellcolor[HTML]{910EA3}{\textcolor{white}{\textbf{9}}} & \cellcolor[HTML]{F1844C}{\textcolor{white}{\textbf{5}}} & \cellcolor[HTML]{E16462}{\textcolor{white}{\textbf{6}}} & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{12}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{4}}}\\
\hspace{1em}Almost daily & \cellcolor[HTML]{D8576B}{\textcolor{white}{\textbf{6}}} & \cellcolor[HTML]{6A00A8}{\textcolor{white}{\textbf{15}}} & \cellcolor[HTML]{D8576B}{\textcolor{white}{\textbf{6}}} & \cellcolor[HTML]{B12A90}{\textcolor{white}{\textbf{10}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}} & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{20}}}\\
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{ride-hailing}}\\
\hspace{1em}Never & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{254}}} & \cellcolor[HTML]{F9983E}{\textcolor{white}{\textbf{13}}} & \cellcolor[HTML]{FB9F3A}{\textcolor{white}{\textbf{6}}} & \cellcolor[HTML]{FBA238}{\textcolor{white}{\textbf{4}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}}\\
\hspace{1em}Rarely & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{192}}} & \cellcolor[HTML]{E56A5D}{\textcolor{white}{\textbf{44}}} & \cellcolor[HTML]{F89540}{\textcolor{white}{\textbf{12}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{1}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{1}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{1}}}\\
\hspace{1em}Once a week & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{60}}} & \cellcolor[HTML]{D35171}{\textcolor{white}{\textbf{20}}} & \cellcolor[HTML]{AC2794}{\textcolor{white}{\textbf{31}}} & \cellcolor[HTML]{F9983E}{\textcolor{white}{\textbf{3}}} & \cellcolor[HTML]{FBA238}{\textcolor{white}{\textbf{1}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}}\\
\hspace{1em}2-3 times per week & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{49}}} & \cellcolor[HTML]{E26561}{\textcolor{white}{\textbf{12}}} & \cellcolor[HTML]{EB7557}{\textcolor{white}{\textbf{9}}} & \cellcolor[HTML]{F07F4F}{\textcolor{white}{\textbf{7}}} & \cellcolor[HTML]{FA9B3D}{\textcolor{white}{\textbf{2}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}}\\
\hspace{1em}4-5 times per week & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{28}}} & \cellcolor[HTML]{D8576B}{\textcolor{white}{\textbf{10}}} & \cellcolor[HTML]{FA9B3D}{\textcolor{white}{\textbf{3}}} & \cellcolor[HTML]{F3874A}{\textcolor{white}{\textbf{5}}} & \cellcolor[HTML]{EF7C51}{\textcolor{white}{\textbf{6}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{2}}}\\
\hspace{1em}Almost daily & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{14}}} & \cellcolor[HTML]{E66C5C}{\textcolor{white}{\textbf{3}}} & \cellcolor[HTML]{DB5C68}{\textcolor{white}{\textbf{4}}} & \cellcolor[HTML]{F79242}{\textcolor{white}{\textbf{1}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}} & \cellcolor[HTML]{F07F4F}{\textcolor{white}{\textbf{2}}}\\
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{rickshaw}}\\
\hspace{1em}Never & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{51}}} & \cellcolor[HTML]{EB7655}{\textcolor{white}{\textbf{9}}} & \cellcolor[HTML]{F3854B}{\textcolor{white}{\textbf{6}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}} & \cellcolor[HTML]{FBA139}{\textcolor{white}{\textbf{1}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}}\\
\hspace{1em}Rarely & \cellcolor[HTML]{340498}{\textcolor{white}{\textbf{64}}} & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{70}}} & \cellcolor[HTML]{E26561}{\textcolor{white}{\textbf{18}}} & \cellcolor[HTML]{F99A3E}{\textcolor{white}{\textbf{4}}} & \cellcolor[HTML]{FA9E3B}{\textcolor{white}{\textbf{3}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{1}}}\\
\hspace{1em}Once a week & \cellcolor[HTML]{6001A6}{\textcolor{white}{\textbf{36}}} & \cellcolor[HTML]{4F02A2}{\textcolor{white}{\textbf{38}}} & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{45}}} & \cellcolor[HTML]{F07F4F}{\textcolor{white}{\textbf{9}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{3}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{3}}}\\
\hspace{1em}2-3 times per week & \cellcolor[HTML]{2C0594}{\textcolor{white}{\textbf{34}}} & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{36}}} & \cellcolor[HTML]{BE3885}{\textcolor{white}{\textbf{18}}} & \cellcolor[HTML]{6100A7}{\textcolor{white}{\textbf{29}}} & \cellcolor[HTML]{F89441}{\textcolor{white}{\textbf{6}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{4}}}\\
\hspace{1em}4-5 times per week & \cellcolor[HTML]{9511A1}{\textcolor{white}{\textbf{21}}} & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{30}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{7}}} & \cellcolor[HTML]{C8437B}{\textcolor{white}{\textbf{16}}} & \cellcolor[HTML]{D04D73}{\textcolor{white}{\textbf{15}}} & \cellcolor[HTML]{F99A3E}{\textcolor{white}{\textbf{8}}}\\
\hspace{1em}Almost daily & \cellcolor[HTML]{99159F}{\textcolor{white}{\textbf{45}}} & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{65}}} & \cellcolor[HTML]{DB5C68}{\textcolor{white}{\textbf{30}}} & \cellcolor[HTML]{FA9B3D}{\textcolor{white}{\textbf{18}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{16}}} & \cellcolor[HTML]{AE2892}{\textcolor{white}{\textbf{41}}}\\
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{CNG auto-rickshaw}}\\
\hspace{1em}Never & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{176}}} & \cellcolor[HTML]{F79044}{\textcolor{white}{\textbf{14}}} & \cellcolor[HTML]{FBA238}{\textcolor{white}{\textbf{3}}} & \cellcolor[HTML]{FCA537}{\textcolor{white}{\textbf{1}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}}\\
\hspace{1em}Rarely & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{213}}} & \cellcolor[HTML]{BE3885}{\textcolor{white}{\textbf{95}}} & \cellcolor[HTML]{F89441}{\textcolor{white}{\textbf{14}}} & \cellcolor[HTML]{FBA238}{\textcolor{white}{\textbf{4}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{1}}} & \cellcolor[HTML]{FCA438}{\textcolor{white}{\textbf{3}}}\\
\hspace{1em}Once a week & \cellcolor[HTML]{280592}{\textcolor{white}{\textbf{36}}} & \cellcolor[HTML]{5901A5}{\textcolor{white}{\textbf{31}}} & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{38}}} & \cellcolor[HTML]{E97158}{\textcolor{white}{\textbf{9}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{2}}} & \cellcolor[HTML]{FA9E3B}{\textcolor{white}{\textbf{3}}}\\
\hspace{1em}2-3 times per week & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{29}}} & \cellcolor[HTML]{9D189D}{\textcolor{white}{\textbf{18}}} & \cellcolor[HTML]{B12A90}{\textcolor{white}{\textbf{16}}} & \cellcolor[HTML]{C23C81}{\textcolor{white}{\textbf{14}}} & \cellcolor[HTML]{E97257}{\textcolor{white}{\textbf{8}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{3}}}\\
\hspace{1em}4-5 times per week & \cellcolor[HTML]{310597}{\textcolor{white}{\textbf{13}}} & \cellcolor[HTML]{CA457A}{\textcolor{white}{\textbf{6}}} & \cellcolor[HTML]{D8576B}{\textcolor{white}{\textbf{5}}} & \cellcolor[HTML]{930FA3}{\textcolor{white}{\textbf{9}}} & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{14}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{1}}}\\
\hspace{1em}Almost daily & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{8}}} & \cellcolor[HTML]{42039E}{\textcolor{white}{\textbf{7}}} & \cellcolor[HTML]{E16462}{\textcolor{white}{\textbf{2}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}} & \cellcolor[HTML]{B12A90}{\textcolor{white}{\textbf{4}}}\\
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{bus}}\\
\hspace{1em}Never & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{116}}} & \cellcolor[HTML]{F79044}{\textcolor{white}{\textbf{9}}} & \cellcolor[HTML]{FA9E3B}{\textcolor{white}{\textbf{3}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}}\\
\hspace{1em}Rarely & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{155}}} & \cellcolor[HTML]{D9586A}{\textcolor{white}{\textbf{46}}} & \cellcolor[HTML]{F89540}{\textcolor{white}{\textbf{9}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}} & \cellcolor[HTML]{FCA438}{\textcolor{white}{\textbf{1}}}\\
\hspace{1em}Once a week & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{73}}} & \cellcolor[HTML]{BE3885}{\textcolor{white}{\textbf{32}}} & \cellcolor[HTML]{D8576B}{\textcolor{white}{\textbf{22}}} & \cellcolor[HTML]{F9973F}{\textcolor{white}{\textbf{4}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}}\\
\hspace{1em}2-3 times per week & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{43}}} & \cellcolor[HTML]{BE3885}{\textcolor{white}{\textbf{19}}} & \cellcolor[HTML]{E06363}{\textcolor{white}{\textbf{11}}} & \cellcolor[HTML]{ED7A53}{\textcolor{white}{\textbf{7}}} & \cellcolor[HTML]{F3854B}{\textcolor{white}{\textbf{5}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}}\\
\hspace{1em}4-5 times per week & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{60}}} & \cellcolor[HTML]{F68E45}{\textcolor{white}{\textbf{6}}} & \cellcolor[HTML]{F79442}{\textcolor{white}{\textbf{5}}} & \cellcolor[HTML]{F9983E}{\textcolor{white}{\textbf{4}}} & \cellcolor[HTML]{E97357}{\textcolor{white}{\textbf{12}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{1}}}\\
\hspace{1em}Almost daily & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{103}}} & \cellcolor[HTML]{E97357}{\textcolor{white}{\textbf{21}}} & \cellcolor[HTML]{F79044}{\textcolor{white}{\textbf{10}}} & \cellcolor[HTML]{F68C45}{\textcolor{white}{\textbf{11}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{2}}} & \cellcolor[HTML]{F79044}{\textcolor{white}{\textbf{10}}}\\
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{motorcycle}}\\
\hspace{1em}Never & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{467}}} & \cellcolor[HTML]{F99A3E}{\textcolor{white}{\textbf{22}}} & \cellcolor[HTML]{FB9F3A}{\textcolor{white}{\textbf{12}}} & \cellcolor[HTML]{FCA537}{\textcolor{white}{\textbf{3}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{1}}} & \cellcolor[HTML]{FBA238}{\textcolor{white}{\textbf{8}}}\\
\hspace{1em}Rarely & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{44}}} & \cellcolor[HTML]{46039F}{\textcolor{white}{\textbf{38}}} & \cellcolor[HTML]{DA5A6A}{\textcolor{white}{\textbf{13}}} & \cellcolor[HTML]{E56A5D}{\textcolor{white}{\textbf{10}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{0}}} & \cellcolor[HTML]{F68C45}{\textcolor{white}{\textbf{4}}}\\
\hspace{1em}Once a week & \cellcolor[HTML]{DF6263}{\textcolor{white}{\textbf{11}}} & \cellcolor[HTML]{DF6263}{\textcolor{white}{\textbf{11}}} & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{34}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{3}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{3}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{3}}}\\
\hspace{1em}2-3 times per week & \cellcolor[HTML]{4B03A1}{\textcolor{white}{\textbf{13}}} & \cellcolor[HTML]{D8576B}{\textcolor{white}{\textbf{6}}} & \cellcolor[HTML]{D8576B}{\textcolor{white}{\textbf{6}}} & \cellcolor[HTML]{0D0887}{\textcolor{white}{\textbf{15}}} & \cellcolor[HTML]{EF7C51}{\textcolor{white}{\textbf{4}}} & \cellcolor[HTML]{FCA636}{\textcolor{white}{\textbf{2}}}\\
